\chapter{Interview Questions}
\label{app:interviews}
\paragraph{Design Evaluation:}
\begin{enumerate}\item Can you describe your design to me? What words best capture what you created?\item How did you decide on this design?\item What stands out to you about this particular design? (What is the first thing that strikes you or comes to mind when you look at it)\item What types of crafts have you made in the past? (if nothing then don’t ask 5)\item How is this design similar to other things you have made in the past? How is it different?\item Do you think your design is beautiful? Why or why not?\end{enumerate}\paragraph{Programing as a Design Tool:}\begin{enumerate}
\item Was the programing enjoyable for you? Why or why not?\item What was useful about using programing to design this bracelet?\item What was difficult or confusing about using programing to design this bracelet?\item Were there things you wished you could have done differently? If so, what?\end{enumerate}\paragraph{Fabrication:}
\begin{enumerate}\item How did the fact that you were designing something you were going to wear affect your design process?\item What was your reaction when you saw your piece come out of the laser cutter?\item What was enjoyable about putting the bracelet together after it was cut? What was difficult?\item Out of the entire process, programing, fabricating and finishing your piece, what did you like the most? What did you like the least?\item What are you going to do with the bracelet once you’re done with it?
\end{enumerate}

\paragraph{Future Motivation:}
\begin{enumerate}\item Would you want to use DressCode for other projects in the future? If so, what sorts of projects would you want to use it for?\item Would you want to use programing and computation for projects in the future? If so, what sorts of projects would you want to use it for?\item Would you want to work with a laser cutter again? If so, what sorts of projects would you want to use it for?
\end{enumerate}
\clearpage
\newpage
