% -*-latex-*-
% 
% For questions, comments, concerns or complaints:
% thesis@mit.edu
% 
%
% $Log: cover.tex,v $
% Revision 1.8  2008/05/13 15:02:15  jdreed
% Degree month is June, not May.  Added note about prevdegrees.
% Arthur Smith's title updated
%
% Revision 1.7  2001/02/08 18:53:16  boojum
% changed some \newpages to \cleardoublepages
%
% Revision 1.6  1999/10/21 14:49:31  boojum
% changed comment referring to documentstyle
%
% Revision 1.5  1999/10/21 14:39:04  boojum
% *** empty log message ***
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.4  1997/04/18  17:54:10  othomas
% added page numbers on abstract and cover, and made 1 abstract
% page the default rather than 2.  (anne hunter tells me this
% is the new institute standard.)
%
% Revision 1.3  93/05/17  17:06:29  starflt
% Added acknowledgements section (suggested by tompalka)
% 
% Revision 1.2  92/04/22  13:13:13  epeisach
% Fixes for 1991 course 6 requirements
% Phrase "and to grant others the right to do so" has been added to 
% permission clause
% Second copy of abstract is not counted as separate pages so numbering works
% out
% 
% Revision 1.1  92/04/22  13:08:20  epeisach

% NOTE:
% These templates make an effort to conform to the MIT Thesis specifications,
% however the specifications can change.  We recommend that you verify the
% layout of your title page with your thesis advisor and/or the MIT 
% Libraries before printing your final copy.
\title{Algorithmic Craft: the Synthesis of Computational Design, Digital Fabrication and Hand Craft}

\author{Jennifer Jacobs}
% If you wish to list your previous degrees on the cover page, use the 
% previous degrees command:
%       \prevdegrees{A.A., Harvard University (1985)}
% You can use the \\ command to list multiple previous degrees
%       \prevdegrees{B.S., University of California (1978) \\
%                    S.M., Massachusetts Institute of Technology (1981)}
\department{Department of Media Arts and Sciences}

% If the thesis is for two degrees simultaneously, list them both
% separated by \and like this:
% \degree{Doctor of Philosophy \and Master of Science}

\prevdegrees{BFA in Digital Arts, \textit{University of Oregon, June 2007} \and MFA in Integrated Media Arts, \textit{Hunter College, Manhattan June 2011}}
 \degree{Master of  Science}
% As of the 2007-08 academic year, valid degree months are September, 
% February, or June.  The default is June.
\degreemonth{September}
\degreeyear{2013}
\thesisdate{June 30th, 2013}

%% By default, the thesis will be copyrighted to MIT.  If you need to copyright
%% the thesis to yourself, just specify the `vi' documentclass option.  If for
%% some reason you want to exactly specify the copyright notice text, you can
%% use the \copyrightnoticetext command.  
%\copyrightnoticetext{Copyright given to author, permission to copy/distribute given to MIT.}

% If there is more than one supervisor, use the \supervisor command
% once for each.
\supervisor{Leah Buechley}{AT\&T Career Development Professor Director, Associate Professor of Media Arts and Sciences,  High-Low Tech Group, MIT Media Lab}
\supervisor{Mitchel Resnick}{ LEGO Papert Professor of Learning Research, Academic Head, Program in Media Arts and Sciences, Director, Lifelong Kindergarten Group, MIT Media Lab}
\supervisor{Neri Oxman}{ Sony Corporation Career Development Professor, Assistant Professor of Media Arts and Sciences, Director, Mediated Matter Group, MIT Media Lab}

% This is the department committee chairman, not the thesis committee
% chairman.  You should replace this with your Department's Committee
% Chairman.
\chairman{...}{Chairman, Department Committee on Graduate Theses}

% Make the titlepage based on the above information.  If you need
% something special and can't use the standard form, you can specify
% the exact text of the titlepage yourself.  Put it in a titlepage
% environment and leave blank lines where you want vertical space.
% The spaces will be adjusted to fill the entire page.  The dotted
% lines for the signatures are made with the \signature command.
\maketitle

% The abstractpage environment sets up everything on the page except
% the text itself.  The title and other header material are put at the
% top of the page, and the supervisors are listed at the bottom.  A
% new page is begun both before and after.  Of course, an abstract may
% be more than one page itself.  If you need more control over the
% format of the page, you can use the abstract environment, which puts
% the word "Abstract" at the beginning and single spaces its text.

%% You can either \input (*not* \include) your abstract file, or you can put
%% the text of the abstract directly between the \begin{abstractpage} and
%% \end{abstractpage} commands.

% First copy: start a new page, and save the page number.
\cleardoublepage
% Uncomment the next line if you do NOT want a page number on your
% abstract and acknowledgments pages.
% \pagestyle{empty}
\setcounter{savepage}{\thepage}
\begin{abstractpage}
\input{abstract}
\end{abstractpage}


\input{quote}

% Additional copy: start a new page, and reset the page number.  This way,
% the second copy of the abstract is not counted as separate pages.
% Uncomment the next 6 lines if you need two copies of the abstract
% page.
% \setcounter{page}{\thesavepage}
% \begin{abstractpage}
% \input{abstract}
% \end{abstractpage}

\cleardoublepage

\section*{Acknowledgments}

Many individuals provided support and guidance through the development of this thesis. I would like to express my gratitude to the following people:I would like to thank my advisor, Leah Buechley, who has been an invaluable mentor and has changed the way I see the world. I would also like to thank my committee members, Mitchel Resnick and Neri Oxman, who both provided insight on how to design creative tools for others.I would like to thank my fellow members of High-Low Tech and the Media Lab Community. To Dave Mellis, for providing vital criticism and for forcing me to question my assumptions. To Sam Jacoby for helping me through self-doubt and for his constant willingness to discuss my ideas. To Emily Lovell, who welcomed me into High-Low Tech and supported my ideas. To Jie Qi and Amit Zoran, for inspiring me through their artistry and craftsmanship. To Sean Follmer for providing frequent feedback on my writing and ideas and encouraging me to take time off. To Ricarose Roque, for helping to facilitate my workshop with young people and for giving valuable advice and feedback on my methods. To my UROPs, Yi Tong, Katie Lee and Hannah Pang, who provided vital assistance in software development. I would also like to thank the participants in my early workshops, Nanwei Gong, Nan Zhao, Lining Yao, Tiffany Tseng, Eric Rosenbaum, Dan Beyer, Elliott Hedman, Scott Gilroy, Felicia Davis, Akane Sano, and many others, who graciously put up with buggy software and a sleep-deprived instructor.Thank you to all the external organizations that helped with the evaluation of this work. To the members of FUSE, specifically Maggie Waldron and Lauren Penney, for all of their feedback and ideas. To Susan Klimczak of Learn 2 Teach, Teach 2 Learn, for helping with my youth workshops. To the wonderful individuals at DreamYard, for hosting us in their studio, and visiting our lab and providing early feedback on the project. I would like to thank my family. To my mom and dad, who gave me with my first sewing kit and my first computer when I was young, and have always encouraged and supported my interest in science and art. Thanks also to my brother, whose own work inspires me to find ways of helping other people express themselves. Lastly, I would like to thank Nicholas Gillian for his support. Thanks for explaining complex algorithms, for listening to my ideas, and for bringing me sandwiches.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% -*-latex-*-
